---
title: "R Notebook"
output: html_notebook
---

The [R plugin](https://www.jetbrains.com/help/pycharm/r-plugin-support.html) for IntelliJ-based IDEs provides
handy capabilities to work with the [R Markdown](https://www.jetbrains.com/help/pycharm/r-markdown.html) files.
To [add](https://www.jetbrains.com/help/pycharm/r-markdown.html#add-code-chunk) a new R chunk,
position the caret at any line or the code chunk, then click "+".

The code chunk appears:
```{r}

if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

#BiocManager::install("tximportData")
#BiocManager::install("tximport")
```


```{r}
library("tximport")
library("readr")
library("tximportData")
library(DESeq2)

```

```{r}
library(tximportData)
dir <- system.file("extdata", package = "tximportData")
list.files(dir)
```
```{r}
samples <- read.table(file.path(dir, "samples.txt"), header = TRUE)
samples
```
Type any R code in the chunk, for example:

```{r}
files <- file.path(dir, "salmon", samples$run, "quant.sf.gz")
names(files) <- paste0("sample", 1:6)
all(file.exists(files))

```
```{r}
library(readr)
tx2gene <- read_csv(file.path(dir, "tx2gene.gencode.v27.csv"))
head(tx2gene)

```
```{r}
library(tximport)
txi <- tximport(files, type = "salmon", tx2gene = tx2gene)
txi.tx <- tximport(files, type = "salmon", txOut = TRUE)
names(txi)
```
```{r}
head(txi$length)
```
```{r}
sampleTable <- data.frame(condition = factor(rep(c("A", "B"), each = 3)))
rownames(sampleTable) <- colnames(txi.tx$counts)
```
```{r}
dds <- DESeqDataSetFromTximport(txi.tx, sampleTable, ~condition)
```
Now, click the **Run** button on the chunk toolbar to [execute](https://www.jetbrains.com/help/pycharm/r-markdown.html#run-r-code) the chunk code. The result should be placed under the chunk.
Click the **Knit and Open Document** to build and preview an output.
