---
title: "R Notebook"
author: ansintsova
date: 28.10.21
output: html_notebook
---

The [R plugin](https://www.jetbrains.com/help/pycharm/r-plugin-support.html) for IntelliJ-based IDEs provides
handy capabilities to work with the [R Markdown](https://www.jetbrains.com/help/pycharm/r-markdown.html) files.
To [add](https://www.jetbrains.com/help/pycharm/r-markdown.html#add-code-chunk) a new R chunk,
position the caret at any line or the code chunk, then click "+".


```{r}
dir <- system.file("extdata", package="tximportData")
samples <- read.table(file.path(dir,"samples.txt"), header=TRUE)
samples$condition <- factor(rep(c("A","B"),each=3))
rownames(samples) <- samples$run
samples[,c("pop","center","run","condition")]
```

```{r}
files <- file.path(dir,"salmon", samples$run, "quant.sf.gz")
names(files) <- samples$run
tx2gene <- read_csv(file.path(dir, "tx2gene.gencode.v27.csv"))

```

```{r}
library(DESeq2)
```
## Load STAR/featureCount data

```{r}
sdf_file <- "data/metadata.csv"
edf_file <- "data/raw_counts.csv"
sdf <- read.csv(sdf_file, row.names=2)
edf <- read.csv(edf_file, row.names=1)
#edf <- subset(edf, select = -c(Length))
edf <- edf[rownames(sdf)]
```

```{r}
head(sdf)
```
```{r}
dds <- DESeqDataSetFromMatrix(countData = edf,
                              colData = sdf,
                              design= ~ condition)
dds
```
```{r}
keep <- rowSums(counts(dds)) >= 10
dds <- dds[keep,]
dds
```
```{r}
dds$condition <- relevel(dds$condition, ref = "Control")
```
```{r}
dds <- DESeq(dds)
```
```{r}

res <- results(dds, contrast=c("condition","Test","Control"))
resSig <- subset(res, abs(log2FoldChange) > 1 & padj < 0.05)
```
```{r}
outDir="data"
write.csv(res, file.path(outDir, paste0("Test_Control", '_unfiltered_results.csv')))
write.csv(resSig, file.path(outDir, paste0("Test_Control", '_filtered_results.csv')))
```

```{r}
vsd <- vst(dds, blind=TRUE)
```
```{r}
plotPCA(vsd, intgroup=c("condition"))
```

```{r}
get_results <- function(dds, c1, c2, outDir){
    res <- results(dds, contrast=c('group', c1, c2), alpha=0.01)
    write.csv(res, file.path(outDir, paste0(c1, '_', c2, '_unfiltered_results.csv')))
    resSig <- subset(res, abs(log2FoldChange) > 1 & padj < 0.01)
    write.csv(resSig, file.path(outDir, paste0(c1, '_', c2, '_filtered_results.csv')))
    print(head(resSig))
    return(res)
}
```

```{r}
resultsNames(dds)
```

```{r}

res2 <- get_results(dds, 'Col0Leaf137', 'Col0axenic', '/data/20_04_2021')
```

```{r}
conditons <- list(c('Col0Leaf137', 'Col0axenic'), c('Col0Leaf15', 'Col0axenic'),
                  c('bak1_bkk1Leaf137', 'bak1_bkk1axenic'), c('bak1_bkk1Leaf15', 'bak1_bkk1axenic'),
                  c('cyp71a12_cyp71a13Leaf137', 'cyp71a12_cyp71a13axenic'), c('cyp71a12_cyp71a13Leaf15', 'cyp71a12_cyp71a13axenic'),
                  c('jar1_ein2_npr1Leaf137', 'jar1_ein2_npr1axenic'), c('jar1_ein2_npr1Leaf15', 'jar1_ein2_npr1axenic'),
                  c('rbohD_rbohFLeaf137', 'rbohD_rbohFaxenic'), c('rbohD_rbohFLeaf15', 'rbohD_rbohFaxenic'),
                  c('exo70b1_exo70b2Leaf137', 'exo70b1_exo70b2axenic'), c('exo70b1_exo70b2Leaf15', 'exo70b1_exo70b2axenic'),
                  c('bik1_pbl1Leaf137', 'bik1_pbl1axenic'), c('bik1_pbl1Leaf15', 'bik1_pbl1axenic'),
                  c('xbat34Leaf137', 'xbat34axenic'), c('xbat34Leaf15', 'xbat34axenic'),
                  c('bak1_bkk1axenic', 'Col0axenic'),
                  c('cyp71a12_cyp71a13axenic', 'Col0axenic'),
                  c('jar1_ein2_npr1axenic', 'Col0axenic'),
                  c('rbohD_rbohFaxenic', 'Col0axenic'),
                  c('exo70b1_exo70b2axenic', 'Col0axenic'),
                  c('bik1_pbl1axenic', 'Col0axenic'),
                  c('xbat34axenic', 'Col0axenic'))


outDir <- '/data/20_04_2021'

for (c in conditons){
  print(c)
  get_results(dds, c[1], c[2], outDir)
}

```


```{r}
leaf_conditons <- list( c('bak1_bkk1Leaf15', 'Col0Leaf15'),
                       c('bak1_bkk1Leaf137', 'Col0Leaf137'),
                       c('cyp71a12_cyp71a13Leaf137', 'Col0Leaf137'),
                       c('cyp71a12_cyp71a13Leaf15', 'Col0Leaf15'),
                       c('jar1_ein2_npr1Leaf137', 'Col0Leaf137'),
                       c('jar1_ein2_npr1Leaf15', 'Col0Leaf15'),
                       c('rbohD_rbohFLeaf137', 'Col0Leaf137'),
                       c('rbohD_rbohFLeaf15', 'Col0Leaf15'),
                       c('exo70b1_exo70b2Leaf137', 'Col0Leaf137'),
                       c('exo70b1_exo70b2Leaf15', 'Col0Leaf15'),
                       c('bik1_pbl1Leaf137',  'Col0Leaf137'),
                       c('bik1_pbl1Leaf15', 'Col0Leaf15'),
                       c('xbat34Leaf137', 'Col0Leaf137'),
                       c('xbat34Leaf15', 'Col0Leaf15'))


outDir <- '/data/25_06_21'

for (c in leaf_conditons){
  print(c)
  get_results(dds, c[1], c[2], outDir)
}

```
```{r}
res2 <- get_results(dds, 'bak1_bkk1Leaf15', 'Col0Leaf15', '/data/25_06_21')
```



```{r}
vsd <- vst(dds)
```
```{r}
write.csv(assay(vsd), file= "/data/vst_normalized_counts.csv")
```

```{r}
?plotPCA
```

```{r}
plotPCA(vsd, intgroup=c("genotype"))
```


```{r}

plotPCA(vsd, intgroup=c("strain"))

```


Now, click the **Run** button on the chunk toolbar to [execute](https://www.jetbrains.com/help/pycharm/r-markdown.html#run-r-code) the chunk code. The result should be placed under the chunk.
Click the **Knit and Open Document** to built and preview an output.